---
title: "04_3_monte_carlo_results"
author: "Suguru Otani"
date: "2024-01-26"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# load {.tabset}

```{r, echo=FALSE,results = "asis"}
rm(list = ls())
library(magrittr)
library(ggplot2)
library(modelsummary) # for N in datasummary
library(here)
num_process_list <-
  c(
    10,
    20,
    30,
    40,
    50,
    100#,
    #500
  )

num_agent_category_list <-
  list(c(20,5),c(20,10),c(20,20),c(20,30))
here::here()
for(i in 1:length(num_agent_category_list)){
  num_agents <- num_agent_category_list[[i]][1]
  num_category <- num_agent_category_list[[i]][2]
  for(nn in 1:length(num_process_list)){
    temp_nn <-
      num_process_list[nn]
    # bias 
    filename <-
      paste(
        "bias_table_",
        "num_process_",
        temp_nn,
        "_num_agents_",
        num_agents,
        "_num_category_",
        num_category,
        #".rds",
        sep = ""
      )
    cat(filename,"\n")
    # load 
    temp_data <-
      readRDS(
        file = 
          here::here(
            paste(
              "output/",
              filename,
              ".rds",
              sep = ""
            )
          )
      )
    assign(
      filename,
      temp_data
      )
    # t-stat
    filename <-
      paste(
        "t_stats_table_",
        "num_process_",
        temp_nn,
        "_num_agents_",
        num_agents,
        "_num_category_",
        num_category,
        #".rds",
        sep = ""
      )
    cat(filename,"\n")
    # load 
    temp_data <-
      readRDS(
        file = 
          here::here(
            paste(
              "output/",
              filename,
              ".rds",
              sep = ""
            )
          )
      )
    assign(
      filename,
      temp_data
      )
    # beta-hat
    filename <-
      paste(
        "beta_hat_table_",
        "num_process_",
        temp_nn,
        "_num_agents_",
        num_agents,
        "_num_category_",
        num_category,
        #".rds",
        sep = ""
      )
    cat(filename,"\n")
    # load 
    temp_data <-
      readRDS(
        file = 
          here::here(
            paste(
              "output/",
              filename,
              ".rds",
              sep = ""
            )
          )
      )
    assign(
      filename,
      temp_data
      )
  }
}

```

The regression model on outcome $Y_{ijt}$ is specified as follows:

$Y_{ijt}=\alpha_{i}+\beta_{j}+\mu_{ij}+\varepsilon_{ijt}$

where $\alpha_{i}$ is worker $i$’s fixed effect, $\beta_{j}$ is category $j$’s fixed effect, $\mu_{ij}$ is $(i,j)$-match effect, and $\varepsilon_{ijt}$ is assumed to be i.i.d standard normal error.

As true DGP, we fix the above parameters as follows:

- $i\in \{1,2,\cdots,20\}$: worker id
- $j\in\{1,2,\cdots,10\}$: category id
- $t\in\{1,2,\cdots,T\}$: we call the number of process
- $\alpha_{i}$= worker id
- $\beta_{j}$= category id
- $\mu_{ij}\sim i.i.d. N(0,1)$+10
- As a result, we have 200 parameters.

Identification

- Worker 1 and Category 1
    - $Y_{11t}=\underbrace{\alpha_{1}+\beta_{1}+\mu_{11}}_{constant}+\varepsilon_{11t}$
- Worker 1 and Category 2
    - $Y_{12t}=\alpha_{1}+\beta_{2}+\mu_{12}+\varepsilon_{12t}\\
    =\underbrace{\alpha_{1}+\beta_{1}+\mu_{11}}_{constant}+\underbrace{(\beta_{2}-\beta_{1})+(\mu_{12}-\mu_{11})}_{category 2 FE}+\varepsilon_{12t}$
- Worker 2 and Category 1
    - $Y_{21t}=\alpha_{2}+\beta_{1}+\mu_{21}+\varepsilon_{21t}\\
    =\underbrace{\alpha_{1}+\beta_{1}+\mu_{11}}_{constant}+\underbrace{(\alpha_{2}-\alpha_{1})+(\mu_{21}-\mu_{11})}_{worker 2 FE}+\varepsilon_{21t}$
- Worker 2 and Category 2
    - $Y_{22t}=\alpha_{2}+\beta_{2}+\mu_{22}+\varepsilon_{22t}\\
    =\underbrace{\alpha_{1}+\beta_{1}+\mu_{11}}_{constant}+\underbrace{(\beta_{2}-\beta_{1})+(\mu_{12}-\mu_{11})}_{category 2 FE}+\underbrace{(\alpha_{2}-\alpha_{1})+(\mu_{21}-\mu_{11})}_{worker 2 FE}+\underbrace{(\mu_{22}+\mu_{11}-\mu_{12}-\mu_{21})}_{(2,2)-match effect}+\varepsilon_{22t}\\
    =\underbrace{\alpha_{1}+\beta_{1}+\mu_{11}}_{constant}+\underbrace{(\beta_{2}-\beta_{1})+(\mu_{12}-\mu_{11})}_{category 2 FE}+\underbrace{(\alpha_{2}-\alpha_{1})+(\mu_{21}-\mu_{11})}_{worker 2 FE}+\underbrace{(\mu_{22}-(\mu_{12}-\mu_{11})-(\mu_{21}-\mu_{11}) -\mu_{11})}_{(2,2)-match effect}+\varepsilon_{22t}$
- In general, Worker $i\neq1$ and Category  $j\neq1$
    - $Y_{ijt}=\alpha_{i}+\beta_{j}+\mu_{ij}+\varepsilon_{ijt}\\
    =\underbrace{\alpha_{1}+\beta_{1}+\mu_{11}}_{constant}+\underbrace{(\beta_{j}-\beta_{1})+(\mu_{1j}-\mu_{11})}_{category j FE}+\underbrace{(\alpha_{i}-\alpha_{1})+(\mu_{i1}-\mu_{11})}_{worker i FE}+\underbrace{(\mu_{ij}+\mu_{11}-\mu_{1j}-\mu_{i1})}_{(i,j)-match effect}+\varepsilon_{ijt}\\
    =\underbrace{\alpha_{1}+\beta_{1}+\mu_{11}}_{constant}+\underbrace{(\beta_{j}-\beta_{1})+(\mu_{1j}-\mu_{11})}_{category j FE}+\underbrace{(\alpha_{i}-\alpha_{1})+(\mu_{i1}-\mu_{11})}_{worker i FE}+\underbrace{(\mu_{ij}-(\mu_{1j}-\mu_{11})-(\mu_{i1}-\mu_{11}) -\mu_{11})}_{(i,j)-match effect}+\varepsilon_{ijt}$
- Therefore,  $\alpha_{i}$ is worker $i$’s fixed effect, $\beta_{j}$ is category $j$’s fixed effect, and $\mu_{ij}$ is $(i,j)$-match effect cannot be identified separately.
- Affinity(相性) is measured by the “relative” fixed effect compared to worker 1 and category 1.


# Bias and power results {.tabset}

Bias should be mean zero. Rejection probability based on t-statistics should be more than 0.8 at significance level $\alpha= 0.05$ for reasonable power (検出力).

## Benchmark data worker=20, category=10 {.tabset}

### num_process = 10, num_simulation = 100 {.tabset}

#### beta hat

```{r,echo=FALSE,results = "asis"}
modelsummary::datasummary_skim(
  fmt = 3,
  beta_hat_table_num_process_10_num_agents_20_num_category_10
  )
```

#### Bias

```{r,echo=FALSE,results = "asis"}
modelsummary::datasummary_skim(
  fmt = 3,
  bias_table_num_process_10_num_agents_20_num_category_10
  )
```

#### Power 

```{r,echo=FALSE,results = "asis"}
num_agent <- 20
num_category <- 10
target_power_table <-
  cbind(
    colnames(t_stats_table_num_process_10_num_agents_20_num_category_10),
    colSums(t_stats_table_num_process_10_num_agents_20_num_category_10 > 1.96)/100
    ) %>% 
  tibble::as_tibble()
colnames(target_power_table) <-
  c(
    "coefficient",
    "rejection_probability"
    )
target_power_table %>% 
  kableExtra::kable() %>% 
  kableExtra::kable_styling()
cat(
  "Significant match effect number =",
  sum(target_power_table$rejection_probability[(num_agent+num_category):(num_agent*num_category)]>0.8),
  " out of ", num_agent*num_category-num_agent-num_category+1
  )
```

### num_process = 20, num_simulation = 100 {.tabset}

#### beta hat

```{r,echo=FALSE,results = "asis"}
modelsummary::datasummary_skim(
  fmt = 3,
  beta_hat_table_num_process_20_num_agents_20_num_category_10
  )
```

#### Bias

```{r,echo=FALSE,results = "asis"}
modelsummary::datasummary_skim(
  fmt = 3,
  bias_table_num_process_20_num_agents_20_num_category_10
  )
```

#### Power 

```{r,echo=FALSE,results = "asis"}
target_power_table <-
  cbind(
    colnames(t_stats_table_num_process_20_num_agents_20_num_category_10),
    colSums(t_stats_table_num_process_20_num_agents_20_num_category_10 > 1.96)/100
    ) %>% 
  tibble::as_tibble()
colnames(target_power_table) <-
  c(
    "coefficient",
    "rejection_probability"
    )
target_power_table %>% 
  kableExtra::kable() %>% 
  kableExtra::kable_styling()
cat(
  "Significant match effect number =",
  sum(target_power_table$rejection_probability[(num_agent+num_category):(num_agent*num_category)]>0.8),
  " out of ", num_agent*num_category-num_agent-num_category+1
  )
```

### num_process = 30, num_simulation = 100 {.tabset}

#### beta hat

```{r,echo=FALSE,results = "asis"}
modelsummary::datasummary_skim(
  fmt = 3,
  beta_hat_table_num_process_30_num_agents_20_num_category_10
  )
```

#### Bias

```{r,echo=FALSE,results = "asis"}
modelsummary::datasummary_skim(
  fmt = 3,
  bias_table_num_process_30_num_agents_20_num_category_10
  )
```

#### Power 

```{r,echo=FALSE,results = "asis"}
target_power_table <-
  cbind(
    colnames(t_stats_table_num_process_30_num_agents_20_num_category_10),
    colSums(t_stats_table_num_process_30_num_agents_20_num_category_10 > 1.96)/100
    ) %>% 
  tibble::as_tibble()
colnames(target_power_table) <-
  c(
    "coefficient",
    "rejection_probability"
    )
target_power_table %>% 
  kableExtra::kable() %>% 
  kableExtra::kable_styling()
cat(
  "Significant match effect number =",
  sum(target_power_table$rejection_probability[(num_agent+num_category):(num_agent*num_category)]>0.8),
  " out of ", num_agent*num_category-num_agent-num_category+1
  )
```

### num_process = 40, num_simulation = 100 {.tabset}

#### beta hat

```{r,echo=FALSE,results = "asis"}
modelsummary::datasummary_skim(
  fmt = 3,
  beta_hat_table_num_process_40_num_agents_20_num_category_10
  )
```

#### Bias

```{r,echo=FALSE,results = "asis"}
modelsummary::datasummary_skim(
  fmt = 3,
  bias_table_num_process_40_num_agents_20_num_category_10
  )
```

#### Power 

```{r,echo=FALSE,results = "asis"}
target_power_table <-
  cbind(
    colnames(t_stats_table_num_process_40_num_agents_20_num_category_10),
    colSums(t_stats_table_num_process_40_num_agents_20_num_category_10 > 1.96)/100
    ) %>% 
  tibble::as_tibble()
colnames(target_power_table) <-
  c(
    "coefficient",
    "rejection_probability"
    )
target_power_table %>% 
  kableExtra::kable() %>% 
  kableExtra::kable_styling()
cat(
  "Significant match effect number =",
  sum(target_power_table$rejection_probability[(num_agent+num_category):(num_agent*num_category)]>0.8),
  " out of ", num_agent*num_category-num_agent-num_category+1
  )
```

### num_process = 50, num_simulation = 100 {.tabset}

#### beta hat

```{r,echo=FALSE,results = "asis"}
modelsummary::datasummary_skim(
  fmt = 3,
  beta_hat_table_num_process_50_num_agents_20_num_category_10
  )
```

#### Bias

```{r,echo=FALSE,results = "asis"}
modelsummary::datasummary_skim(
  fmt = 3,
  bias_table_num_process_50_num_agents_20_num_category_10
  )
```

#### Power 

```{r,echo=FALSE,results = "asis"}
target_power_table <-
  cbind(
    colnames(t_stats_table_num_process_50_num_agents_20_num_category_10),
    colSums(t_stats_table_num_process_50_num_agents_20_num_category_10 > 1.96)/100
    ) %>% 
  tibble::as_tibble()
colnames(target_power_table) <-
  c(
    "coefficient",
    "rejection_probability"
    )
target_power_table %>% 
  kableExtra::kable() %>% 
  kableExtra::kable_styling()
cat(
  "Significant match effect number =",
  sum(target_power_table$rejection_probability[(num_agent+num_category):(num_agent*num_category)]>0.8),
  " out of ", num_agent*num_category-num_agent-num_category+1
  )
```

### num_process = 100, num_simulation = 100 {.tabset}

#### beta hat

```{r,echo=FALSE,results = "asis"}
modelsummary::datasummary_skim(
  fmt = 3,
  beta_hat_table_num_process_100_num_agents_20_num_category_10
  )
```

#### Bias

```{r,echo=FALSE,results = "asis"}
modelsummary::datasummary_skim(
  fmt = 3,
  bias_table_num_process_100_num_agents_20_num_category_10
  )
```

#### Power 

```{r,echo=FALSE,results = "asis"}
target_power_table <-
  cbind(
    colnames(t_stats_table_num_process_100_num_agents_20_num_category_10),
    colSums(t_stats_table_num_process_100_num_agents_20_num_category_10 > 1.96)/100
    ) %>% 
  tibble::as_tibble()
colnames(target_power_table) <-
  c(
    "coefficient",
    "rejection_probability"
    )
target_power_table %>% 
  kableExtra::kable() %>% 
  kableExtra::kable_styling()
cat(
  "Significant match effect number =",
  sum(target_power_table$rejection_probability[(num_agent+num_category):(num_agent*num_category)]>0.8),
  " out of ", num_agent*num_category-num_agent-num_category+1
  )
```

## worker=20, category=5 {.tabset}

### num_process = 10, num_simulation = 100 {.tabset}

#### beta hat

```{r,echo=FALSE,results = "asis"}
num_agent <- 20
num_category <- 5
modelsummary::datasummary_skim(
  fmt = 3,
  beta_hat_table_num_process_10_num_agents_20_num_category_5
  )
```

#### Bias

```{r,echo=FALSE,results = "asis"}
modelsummary::datasummary_skim(
  fmt = 3,
  bias_table_num_process_10_num_agents_20_num_category_5
  )
```

#### Power 

```{r,echo=FALSE,results = "asis"}
target_power_table <-
  cbind(
    colnames(t_stats_table_num_process_10_num_agents_20_num_category_5),
    colSums(t_stats_table_num_process_10_num_agents_20_num_category_5 > 1.96)/100
    ) %>% 
  tibble::as_tibble()
colnames(target_power_table) <-
  c(
    "coefficient",
    "rejection_probability"
    )
target_power_table %>% 
  kableExtra::kable() %>% 
  kableExtra::kable_styling()
cat(
  "Significant match effect number =",
  sum(target_power_table$rejection_probability[(num_agent+num_category):(num_agent*num_category)]>0.8),
  " out of ", num_agent*num_category-num_agent-num_category+1
  )
```

### num_process = 20, num_simulation = 100 {.tabset}

#### beta hat

```{r,echo=FALSE,results = "asis"}
modelsummary::datasummary_skim(
  fmt = 3,
  beta_hat_table_num_process_20_num_agents_20_num_category_5
  )
```

#### Bias

```{r,echo=FALSE,results = "asis"}
modelsummary::datasummary_skim(
  fmt = 3,
  bias_table_num_process_20_num_agents_20_num_category_5
  )
```

#### Power 

```{r,echo=FALSE,results = "asis"}
target_power_table <-
  cbind(
    colnames(t_stats_table_num_process_20_num_agents_20_num_category_5),
    colSums(t_stats_table_num_process_20_num_agents_20_num_category_5 > 1.96)/100
    ) %>% 
  tibble::as_tibble()
colnames(target_power_table) <-
  c(
    "coefficient",
    "rejection_probability"
    )
target_power_table %>% 
  kableExtra::kable() %>% 
  kableExtra::kable_styling()
cat(
  "Significant match effect number =",
  sum(target_power_table$rejection_probability[(num_agent+num_category):(num_agent*num_category)]>0.8),
  " out of ", num_agent*num_category-num_agent-num_category+1
  )
```

### num_process = 30, num_simulation = 100 {.tabset}

#### beta hat

```{r,echo=FALSE,results = "asis"}
modelsummary::datasummary_skim(
  fmt = 3,
  beta_hat_table_num_process_30_num_agents_20_num_category_5
  )
```

#### Bias

```{r,echo=FALSE,results = "asis"}
modelsummary::datasummary_skim(
  fmt = 3,
  bias_table_num_process_30_num_agents_20_num_category_5
  )
```

#### Power 

```{r,echo=FALSE,results = "asis"}
target_power_table <-
  cbind(
    colnames(t_stats_table_num_process_30_num_agents_20_num_category_5),
    colSums(t_stats_table_num_process_30_num_agents_20_num_category_5 > 1.96)/100
    ) %>% 
  tibble::as_tibble()
colnames(target_power_table) <-
  c(
    "coefficient",
    "rejection_probability"
    )
target_power_table %>% 
  kableExtra::kable() %>% 
  kableExtra::kable_styling()
cat(
  "Significant match effect number =",
  sum(target_power_table$rejection_probability[(num_agent+num_category):(num_agent*num_category)]>0.8),
  " out of ", num_agent*num_category-num_agent-num_category+1
  )
```

### num_process = 40, num_simulation = 100 {.tabset}

#### beta hat

```{r,echo=FALSE,results = "asis"}
modelsummary::datasummary_skim(
  fmt = 3,
  beta_hat_table_num_process_40_num_agents_20_num_category_5
  )
```

#### Bias

```{r,echo=FALSE,results = "asis"}
modelsummary::datasummary_skim(
  fmt = 3,
  bias_table_num_process_40_num_agents_20_num_category_5
  )
```

#### Power 

```{r,echo=FALSE,results = "asis"}
target_power_table <-
  cbind(
    colnames(t_stats_table_num_process_40_num_agents_20_num_category_5),
    colSums(t_stats_table_num_process_40_num_agents_20_num_category_5 > 1.96)/100
    ) %>% 
  tibble::as_tibble()
colnames(target_power_table) <-
  c(
    "coefficient",
    "rejection_probability"
    )
target_power_table %>% 
  kableExtra::kable() %>% 
  kableExtra::kable_styling()
cat(
  "Significant match effect number =",
  sum(target_power_table$rejection_probability[(num_agent+num_category):(num_agent*num_category)]>0.8),
  " out of ", num_agent*num_category-num_agent-num_category+1
  )
```

### num_process = 50, num_simulation = 100 {.tabset}

#### beta hat

```{r,echo=FALSE,results = "asis"}
modelsummary::datasummary_skim(
  fmt = 3,
  beta_hat_table_num_process_50_num_agents_20_num_category_5
  )
```

#### Bias

```{r,echo=FALSE,results = "asis"}
modelsummary::datasummary_skim(
  fmt = 3,
  bias_table_num_process_50_num_agents_20_num_category_5
  )
```

#### Power 

```{r,echo=FALSE,results = "asis"}
target_power_table <-
  cbind(
    colnames(t_stats_table_num_process_50_num_agents_20_num_category_5),
    colSums(t_stats_table_num_process_50_num_agents_20_num_category_5 > 1.96)/100
    ) %>% 
  tibble::as_tibble()
colnames(target_power_table) <-
  c(
    "coefficient",
    "rejection_probability"
    )
target_power_table %>% 
  kableExtra::kable() %>% 
  kableExtra::kable_styling()
cat(
  "Significant match effect number =",
  sum(target_power_table$rejection_probability[(num_agent+num_category):(num_agent*num_category)]>0.8),
  " out of ", num_agent*num_category-num_agent-num_category+1
  )
```

### num_process = 100, num_simulation = 100 {.tabset}

#### beta hat

```{r,echo=FALSE,results = "asis"}
modelsummary::datasummary_skim(
  fmt = 3,
  beta_hat_table_num_process_100_num_agents_20_num_category_5
  )
```

#### Bias

```{r,echo=FALSE,results = "asis"}
modelsummary::datasummary_skim(
  fmt = 3,
  bias_table_num_process_100_num_agents_20_num_category_5
  )
```

#### Power 

```{r,echo=FALSE,results = "asis"}
target_power_table <-
  cbind(
    colnames(t_stats_table_num_process_100_num_agents_20_num_category_5),
    colSums(t_stats_table_num_process_100_num_agents_20_num_category_5 > 1.96)/100
    ) %>% 
  tibble::as_tibble()
colnames(target_power_table) <-
  c(
    "coefficient",
    "rejection_probability"
    )
target_power_table %>% 
  kableExtra::kable() %>% 
  kableExtra::kable_styling()
cat(
  "Significant match effect number =",
  sum(target_power_table$rejection_probability[(num_agent+num_category):(num_agent*num_category)]>0.8),
  " out of ", num_agent*num_category-num_agent-num_category+1
  )
```

## worker=20, category=10 {.tabset}

### num_process = 10, num_simulation = 100 {.tabset}

#### beta hat

```{r,echo=FALSE,results = "asis"}
num_agent <- 20
num_category <- 10
modelsummary::datasummary_skim(
  fmt = 3,
  beta_hat_table_num_process_10_num_agents_20_num_category_10
  )
```

#### Bias

```{r,echo=FALSE,results = "asis"}
modelsummary::datasummary_skim(
  fmt = 3,
  bias_table_num_process_10_num_agents_20_num_category_10
  )
```

#### Power 

```{r,echo=FALSE,results = "asis"}
target_power_table <-
  cbind(
    colnames(t_stats_table_num_process_10_num_agents_20_num_category_10),
    colSums(t_stats_table_num_process_10_num_agents_20_num_category_10 > 1.96)/100
    ) %>% 
  tibble::as_tibble()
colnames(target_power_table) <-
  c(
    "coefficient",
    "rejection_probability"
    )
target_power_table %>% 
  kableExtra::kable() %>% 
  kableExtra::kable_styling()
cat(
  "Significant match effect number =",
  sum(target_power_table$rejection_probability[(num_agent+num_category):(num_agent*num_category)]>0.8),
  " out of ", num_agent*num_category-num_agent-num_category+1
  )
```

### num_process = 20, num_simulation = 100 {.tabset}

#### beta hat

```{r,echo=FALSE,results = "asis"}
modelsummary::datasummary_skim(
  fmt = 3,
  beta_hat_table_num_process_20_num_agents_20_num_category_10
  )
```

#### Bias

```{r,echo=FALSE,results = "asis"}
modelsummary::datasummary_skim(
  fmt = 3,
  bias_table_num_process_20_num_agents_20_num_category_10
  )
```

#### Power 

```{r,echo=FALSE,results = "asis"}
target_power_table <-
  cbind(
    colnames(t_stats_table_num_process_20_num_agents_20_num_category_10),
    colSums(t_stats_table_num_process_20_num_agents_20_num_category_10 > 1.96)/100
    ) %>% 
  tibble::as_tibble()
colnames(target_power_table) <-
  c(
    "coefficient",
    "rejection_probability"
    )
target_power_table %>% 
  kableExtra::kable() %>% 
  kableExtra::kable_styling()
cat(
  "Significant match effect number =",
  sum(target_power_table$rejection_probability[(num_agent+num_category):(num_agent*num_category)]>0.8),
  " out of ", num_agent*num_category-num_agent-num_category+1
  )
```

### num_process = 30, num_simulation = 100 {.tabset}

#### beta hat

```{r,echo=FALSE,results = "asis"}
modelsummary::datasummary_skim(
  fmt = 3,
  beta_hat_table_num_process_30_num_agents_20_num_category_10
  )
```

#### Bias

```{r,echo=FALSE,results = "asis"}
modelsummary::datasummary_skim(
  fmt = 3,
  bias_table_num_process_30_num_agents_20_num_category_10
  )
```

#### Power 

```{r,echo=FALSE,results = "asis"}
target_power_table <-
  cbind(
    colnames(t_stats_table_num_process_30_num_agents_20_num_category_10),
    colSums(t_stats_table_num_process_30_num_agents_20_num_category_10 > 1.96)/100
    ) %>% 
  tibble::as_tibble()
colnames(target_power_table) <-
  c(
    "coefficient",
    "rejection_probability"
    )
target_power_table %>% 
  kableExtra::kable() %>% 
  kableExtra::kable_styling()
cat(
  "Significant match effect number =",
  sum(target_power_table$rejection_probability[(num_agent+num_category):(num_agent*num_category)]>0.8),
  " out of ", num_agent*num_category-num_agent-num_category+1
  )
```

### num_process = 40, num_simulation = 100 {.tabset}

#### beta hat

```{r,echo=FALSE,results = "asis"}
modelsummary::datasummary_skim(
  fmt = 3,
  beta_hat_table_num_process_40_num_agents_20_num_category_10
  )
```

#### Bias

```{r,echo=FALSE,results = "asis"}
modelsummary::datasummary_skim(
  fmt = 3,
  bias_table_num_process_40_num_agents_20_num_category_10
  )
```

#### Power 

```{r,echo=FALSE,results = "asis"}
target_power_table <-
  cbind(
    colnames(t_stats_table_num_process_40_num_agents_20_num_category_10),
    colSums(t_stats_table_num_process_40_num_agents_20_num_category_10 > 1.96)/100
    ) %>% 
  tibble::as_tibble()
colnames(target_power_table) <-
  c(
    "coefficient",
    "rejection_probability"
    )
target_power_table %>% 
  kableExtra::kable() %>% 
  kableExtra::kable_styling()
cat(
  "Significant match effect number =",
  sum(target_power_table$rejection_probability[(num_agent+num_category):(num_agent*num_category)]>0.8),
  " out of ", num_agent*num_category-num_agent-num_category+1
  )
```

### num_process = 50, num_simulation = 100 {.tabset}

#### beta hat

```{r,echo=FALSE,results = "asis"}
modelsummary::datasummary_skim(
  fmt = 3,
  beta_hat_table_num_process_50_num_agents_20_num_category_10
  )
```

#### Bias

```{r,echo=FALSE,results = "asis"}
modelsummary::datasummary_skim(
  fmt = 3,
  bias_table_num_process_50_num_agents_20_num_category_10
  )
```

#### Power 

```{r,echo=FALSE,results = "asis"}
target_power_table <-
  cbind(
    colnames(t_stats_table_num_process_50_num_agents_20_num_category_10),
    colSums(t_stats_table_num_process_50_num_agents_20_num_category_10 > 1.96)/100
    ) %>% 
  tibble::as_tibble()
colnames(target_power_table) <-
  c(
    "coefficient",
    "rejection_probability"
    )
target_power_table %>% 
  kableExtra::kable() %>% 
  kableExtra::kable_styling()
cat(
  "Significant match effect number =",
  sum(target_power_table$rejection_probability[(num_agent+num_category):(num_agent*num_category)]>0.8),
  " out of ", num_agent*num_category-num_agent-num_category+1
  )
```

### num_process = 100, num_simulation = 100 {.tabset}

#### beta hat

```{r,echo=FALSE,results = "asis"}
modelsummary::datasummary_skim(
  fmt = 3,
  beta_hat_table_num_process_100_num_agents_20_num_category_10
  )
```

#### Bias

```{r,echo=FALSE,results = "asis"}
modelsummary::datasummary_skim(
  fmt = 3,
  bias_table_num_process_100_num_agents_20_num_category_10
  )
```

#### Power 

```{r,echo=FALSE,results = "asis"}
target_power_table <-
  cbind(
    colnames(t_stats_table_num_process_100_num_agents_20_num_category_10),
    colSums(t_stats_table_num_process_100_num_agents_20_num_category_10 > 1.96)/100
    ) %>% 
  tibble::as_tibble()
colnames(target_power_table) <-
  c(
    "coefficient",
    "rejection_probability"
    )
target_power_table %>% 
  kableExtra::kable() %>% 
  kableExtra::kable_styling()
cat(
  "Significant match effect number =",
  sum(target_power_table$rejection_probability[(num_agent+num_category):(num_agent*num_category)]>0.8),
  " out of ", num_agent*num_category-num_agent-num_category+1
  )
```

## worker=20, category=20 {.tabset}

### num_process = 10, num_simulation = 100 {.tabset}

#### beta hat

```{r,echo=FALSE,results = "asis"}
num_agent <- 20
num_category <- 20
modelsummary::datasummary_skim(
  fmt = 3,
  beta_hat_table_num_process_10_num_agents_20_num_category_20[1:250]
  )
modelsummary::datasummary_skim(
  fmt = 3,
  beta_hat_table_num_process_10_num_agents_20_num_category_20[251:(num_agent*num_category)]
  )
```

#### Bias

```{r,echo=FALSE,results = "asis"}
modelsummary::datasummary_skim(
  fmt = 3,
  bias_table_num_process_10_num_agents_20_num_category_20[1:250]
  )
modelsummary::datasummary_skim(
  fmt = 3,
  bias_table_num_process_10_num_agents_20_num_category_20[251:(num_agent*num_category)]
  )
```

#### Power 

```{r,echo=FALSE,results = "asis"}
target_power_table <-
  cbind(
    colnames(t_stats_table_num_process_10_num_agents_20_num_category_20),
    colSums(t_stats_table_num_process_10_num_agents_20_num_category_20 > 1.96)/100
    ) %>% 
  tibble::as_tibble()
colnames(target_power_table) <-
  c(
    "coefficient",
    "rejection_probability"
    )
target_power_table %>% 
  kableExtra::kable() %>% 
  kableExtra::kable_styling()
cat(
  "Significant match effect number =",
  sum(target_power_table$rejection_probability[(num_agent+num_category):(num_agent*num_category)]>0.8),
  " out of ", num_agent*num_category-num_agent-num_category+1
  )
```

### num_process = 20, num_simulation = 100 {.tabset}

#### beta hat

```{r,echo=FALSE,results = "asis"}
modelsummary::datasummary_skim(
  fmt = 3,
  beta_hat_table_num_process_20_num_agents_20_num_category_20[1:250]
  )
modelsummary::datasummary_skim(
  fmt = 3,
  beta_hat_table_num_process_20_num_agents_20_num_category_20[251:(num_agent*num_category)]
  )
```

#### Bias

```{r,echo=FALSE,results = "asis"}
modelsummary::datasummary_skim(
  fmt = 3,
  bias_table_num_process_20_num_agents_20_num_category_20[1:250]
  )
modelsummary::datasummary_skim(
  fmt = 3,
  bias_table_num_process_20_num_agents_20_num_category_20[251:(num_agent*num_category)]
  )
```

#### Power 

```{r,echo=FALSE,results = "asis"}
target_power_table <-
  cbind(
    colnames(t_stats_table_num_process_20_num_agents_20_num_category_20),
    colSums(t_stats_table_num_process_20_num_agents_20_num_category_20 > 1.96)/100
    ) %>% 
  tibble::as_tibble()
colnames(target_power_table) <-
  c(
    "coefficient",
    "rejection_probability"
    )
target_power_table %>% 
  kableExtra::kable() %>% 
  kableExtra::kable_styling()
cat(
  "Significant match effect number =",
  sum(target_power_table$rejection_probability[(num_agent+num_category):(num_agent*num_category)]>0.8),
  " out of ", num_agent*num_category-num_agent-num_category+1
  )
```

### num_process = 30, num_simulation = 100 {.tabset}

#### beta hat

```{r,echo=FALSE,results = "asis"}
modelsummary::datasummary_skim(
  fmt = 3,
  beta_hat_table_num_process_30_num_agents_20_num_category_20[1:250]
  )
modelsummary::datasummary_skim(
  fmt = 3,
  beta_hat_table_num_process_30_num_agents_20_num_category_20[251:(num_agent*num_category)]
  )
```

#### Bias

```{r,echo=FALSE,results = "asis"}
modelsummary::datasummary_skim(
  fmt = 3,
  bias_table_num_process_30_num_agents_20_num_category_20[1:250]
  )
modelsummary::datasummary_skim(
  fmt = 3,
  bias_table_num_process_30_num_agents_20_num_category_20[251:(num_agent*num_category)]
  )
```

#### Power 

```{r,echo=FALSE,results = "asis"}
target_power_table <-
  cbind(
    colnames(t_stats_table_num_process_30_num_agents_20_num_category_20),
    colSums(t_stats_table_num_process_30_num_agents_20_num_category_20 > 1.96)/100
    ) %>% 
  tibble::as_tibble()
colnames(target_power_table) <-
  c(
    "coefficient",
    "rejection_probability"
    )
target_power_table %>% 
  kableExtra::kable() %>% 
  kableExtra::kable_styling()
cat(
  "Significant match effect number =",
  sum(target_power_table$rejection_probability[(num_agent+num_category):(num_agent*num_category)]>0.8),
  " out of ", num_agent*num_category-num_agent-num_category+1
  )
```

### num_process = 40, num_simulation = 100 {.tabset}

#### beta hat

```{r,echo=FALSE,results = "asis"}
modelsummary::datasummary_skim(
  fmt = 3,
  beta_hat_table_num_process_40_num_agents_20_num_category_20[1:250]
  )
modelsummary::datasummary_skim(
  fmt = 3,
  beta_hat_table_num_process_40_num_agents_20_num_category_20[251:(num_agent*num_category)]
  )
```

#### Bias

```{r,echo=FALSE,results = "asis"}
modelsummary::datasummary_skim(
  fmt = 3,
  bias_table_num_process_40_num_agents_20_num_category_20[1:250]
  )
modelsummary::datasummary_skim(
  fmt = 3,
  bias_table_num_process_40_num_agents_20_num_category_20[251:(num_agent*num_category)]
  )
```

#### Power 

```{r,echo=FALSE,results = "asis"}
target_power_table <-
  cbind(
    colnames(t_stats_table_num_process_40_num_agents_20_num_category_20),
    colSums(t_stats_table_num_process_40_num_agents_20_num_category_20 > 1.96)/100
    ) %>% 
  tibble::as_tibble()
colnames(target_power_table) <-
  c(
    "coefficient",
    "rejection_probability"
    )
target_power_table %>% 
  kableExtra::kable() %>% 
  kableExtra::kable_styling()
cat(
  "Significant match effect number =",
  sum(target_power_table$rejection_probability[(num_agent+num_category):(num_agent*num_category)]>0.8),
  " out of ", num_agent*num_category-num_agent-num_category+1
  )
```

### num_process = 50, num_simulation = 100 {.tabset}

#### beta hat

```{r,echo=FALSE,results = "asis"}
modelsummary::datasummary_skim(
  fmt = 3,
  beta_hat_table_num_process_50_num_agents_20_num_category_20[1:250]
  )
modelsummary::datasummary_skim(
  fmt = 3,
  beta_hat_table_num_process_50_num_agents_20_num_category_20[251:(num_agent*num_category)]
  )
```

#### Bias

```{r,echo=FALSE,results = "asis"}
modelsummary::datasummary_skim(
  fmt = 3,
  bias_table_num_process_50_num_agents_20_num_category_20[1:250]
  )
modelsummary::datasummary_skim(
  fmt = 3,
  bias_table_num_process_50_num_agents_20_num_category_20[251:(num_agent*num_category)]
  )
```

#### Power 

```{r,echo=FALSE,results = "asis"}
target_power_table <-
  cbind(
    colnames(t_stats_table_num_process_50_num_agents_20_num_category_20),
    colSums(t_stats_table_num_process_50_num_agents_20_num_category_20 > 1.96)/100
    ) %>% 
  tibble::as_tibble()
colnames(target_power_table) <-
  c(
    "coefficient",
    "rejection_probability"
    )
target_power_table %>% 
  kableExtra::kable() %>% 
  kableExtra::kable_styling()
cat(
  "Significant match effect number =",
  sum(target_power_table$rejection_probability[(num_agent+num_category):(num_agent*num_category)]>0.8),
  " out of ", num_agent*num_category-num_agent-num_category+1
  )
```

### num_process = 100, num_simulation = 100 {.tabset}

#### beta hat

```{r,echo=FALSE,results = "asis"}
modelsummary::datasummary_skim(
  fmt = 3,
  beta_hat_table_num_process_100_num_agents_20_num_category_20[1:250]
  )
modelsummary::datasummary_skim(
  fmt = 3,
  beta_hat_table_num_process_100_num_agents_20_num_category_20[251:(num_agent*num_category)]
  )
```

#### Bias

```{r,echo=FALSE,results = "asis"}
modelsummary::datasummary_skim(
  fmt = 3,
  bias_table_num_process_100_num_agents_20_num_category_20[1:250]
  )
modelsummary::datasummary_skim(
  fmt = 3,
  bias_table_num_process_100_num_agents_20_num_category_20[251:(num_agent*num_category)]
  )
```

#### Power 

```{r,echo=FALSE,results = "asis"}
target_power_table <-
  cbind(
    colnames(t_stats_table_num_process_100_num_agents_20_num_category_20),
    colSums(t_stats_table_num_process_100_num_agents_20_num_category_20 > 1.96)/100
    ) %>% 
  tibble::as_tibble()
colnames(target_power_table) <-
  c(
    "coefficient",
    "rejection_probability"
    )
target_power_table %>% 
  kableExtra::kable() %>% 
  kableExtra::kable_styling()
cat(
  "Significant match effect number =",
  sum(target_power_table$rejection_probability[(num_agent+num_category):(num_agent*num_category)]>0.8),
  " out of ", num_agent*num_category-num_agent-num_category+1
  )
```

## worker=20, category=30 {.tabset}

### num_process = 10, num_simulation = 100 {.tabset}

#### beta hat

```{r,echo=FALSE,results = "asis"}
num_agent <- 20
num_category <- 30
modelsummary::datasummary_skim(
  fmt = 3,
  beta_hat_table_num_process_10_num_agents_20_num_category_30[1:250]
  )
modelsummary::datasummary_skim(
  fmt = 3,
  beta_hat_table_num_process_10_num_agents_20_num_category_30[251:500]
  )
modelsummary::datasummary_skim(
  fmt = 3,
  beta_hat_table_num_process_10_num_agents_20_num_category_30[501:(num_agent*num_category)]
  )
```

#### Bias

```{r,echo=FALSE,results = "asis"}
modelsummary::datasummary_skim(
  fmt = 3,
  bias_table_num_process_10_num_agents_20_num_category_30[1:250]
  )
modelsummary::datasummary_skim(
  fmt = 3,
  bias_table_num_process_10_num_agents_20_num_category_30[251:500]
  )
modelsummary::datasummary_skim(
  fmt = 3,
  bias_table_num_process_10_num_agents_20_num_category_30[501:(num_agent*num_category)]
  )
```

#### Power 

```{r,echo=FALSE,results = "asis"}
target_power_table <-
  cbind(
    colnames(t_stats_table_num_process_10_num_agents_20_num_category_30),
    colSums(t_stats_table_num_process_10_num_agents_20_num_category_30 > 1.96)/100
    ) %>% 
  tibble::as_tibble()
colnames(target_power_table) <-
  c(
    "coefficient",
    "rejection_probability"
    )
target_power_table %>% 
  kableExtra::kable() %>% 
  kableExtra::kable_styling()
cat(
  "Significant match effect number =",
  sum(target_power_table$rejection_probability[(num_agent+num_category):(num_agent*num_category)]>0.8),
  " out of ", num_agent*num_category-num_agent-num_category+1
  )
```

### num_process = 20, num_simulation = 100 {.tabset}

#### beta hat

```{r,echo=FALSE,results = "asis"}
modelsummary::datasummary_skim(
  fmt = 3,
  beta_hat_table_num_process_20_num_agents_20_num_category_30[1:250]
  )
modelsummary::datasummary_skim(
  fmt = 3,
  beta_hat_table_num_process_20_num_agents_20_num_category_30[251:500]
  )
modelsummary::datasummary_skim(
  fmt = 3,
  beta_hat_table_num_process_20_num_agents_20_num_category_30[501:(num_agent*num_category)]
  )
```

#### Bias

```{r,echo=FALSE,results = "asis"}
modelsummary::datasummary_skim(
  fmt = 3,
  bias_table_num_process_20_num_agents_20_num_category_30[1:250]
  )
modelsummary::datasummary_skim(
  fmt = 3,
  bias_table_num_process_20_num_agents_20_num_category_30[251:500]
  )
modelsummary::datasummary_skim(
  fmt = 3,
  bias_table_num_process_20_num_agents_20_num_category_30[501:(num_agent*num_category)]
  )
```

#### Power 

```{r,echo=FALSE,results = "asis"}
target_power_table <-
  cbind(
    colnames(t_stats_table_num_process_20_num_agents_20_num_category_30),
    colSums(t_stats_table_num_process_20_num_agents_20_num_category_30 > 1.96)/100
    ) %>% 
  tibble::as_tibble()
colnames(target_power_table) <-
  c(
    "coefficient",
    "rejection_probability"
    )
target_power_table %>% 
  kableExtra::kable() %>% 
  kableExtra::kable_styling()
cat(
  "Significant match effect number =",
  sum(target_power_table$rejection_probability[(num_agent+num_category):(num_agent*num_category)]>0.8),
  " out of ", num_agent*num_category-num_agent-num_category+1
  )
```

### num_process = 30, num_simulation = 100 {.tabset}

#### beta hat

```{r,echo=FALSE,results = "asis"}
modelsummary::datasummary_skim(
  fmt = 3,
  beta_hat_table_num_process_30_num_agents_20_num_category_30[1:250]
  )
modelsummary::datasummary_skim(
  fmt = 3,
  beta_hat_table_num_process_30_num_agents_20_num_category_30[251:500]
  )
modelsummary::datasummary_skim(
  fmt = 3,
  beta_hat_table_num_process_30_num_agents_20_num_category_30[501:(num_agent*num_category)]
  )
```

#### Bias

```{r,echo=FALSE,results = "asis"}
modelsummary::datasummary_skim(
  fmt = 3,
  bias_table_num_process_30_num_agents_20_num_category_30[1:250]
  )
modelsummary::datasummary_skim(
  fmt = 3,
  bias_table_num_process_30_num_agents_20_num_category_30[251:500]
  )
modelsummary::datasummary_skim(
  fmt = 3,
  bias_table_num_process_30_num_agents_20_num_category_30[501:(num_agent*num_category)]
  )
```

#### Power 

```{r,echo=FALSE,results = "asis"}
target_power_table <-
  cbind(
    colnames(t_stats_table_num_process_30_num_agents_20_num_category_30),
    colSums(t_stats_table_num_process_30_num_agents_20_num_category_30 > 1.96)/100
    ) %>% 
  tibble::as_tibble()
colnames(target_power_table) <-
  c(
    "coefficient",
    "rejection_probability"
    )
target_power_table %>% 
  kableExtra::kable() %>% 
  kableExtra::kable_styling()
cat(
  "Significant match effect number =",
  sum(target_power_table$rejection_probability[(num_agent+num_category):(num_agent*num_category)]>0.8),
  " out of ", num_agent*num_category-num_agent-num_category+1
  )
```

### num_process = 40, num_simulation = 100 {.tabset}

#### beta hat

```{r,echo=FALSE,results = "asis"}
modelsummary::datasummary_skim(
  fmt = 3,
  beta_hat_table_num_process_40_num_agents_20_num_category_30[1:250]
  )
modelsummary::datasummary_skim(
  fmt = 3,
  beta_hat_table_num_process_40_num_agents_20_num_category_30[251:500]
  )
modelsummary::datasummary_skim(
  fmt = 3,
  beta_hat_table_num_process_40_num_agents_20_num_category_30[501:(num_agent*num_category)]
  )
```

#### Bias

```{r,echo=FALSE,results = "asis"}
modelsummary::datasummary_skim(
  fmt = 3,
  bias_table_num_process_40_num_agents_20_num_category_30[1:250]
  )
modelsummary::datasummary_skim(
  fmt = 3,
  bias_table_num_process_40_num_agents_20_num_category_30[251:500]
  )
modelsummary::datasummary_skim(
  fmt = 3,
  bias_table_num_process_40_num_agents_20_num_category_30[501:(num_agent*num_category)]
  )
```

#### Power 

```{r,echo=FALSE,results = "asis"}
target_power_table <-
  cbind(
    colnames(t_stats_table_num_process_40_num_agents_20_num_category_30),
    colSums(t_stats_table_num_process_40_num_agents_20_num_category_30 > 1.96)/100
    ) %>% 
  tibble::as_tibble()
colnames(target_power_table) <-
  c(
    "coefficient",
    "rejection_probability"
    )
target_power_table %>% 
  kableExtra::kable() %>% 
  kableExtra::kable_styling()
cat(
  "Significant match effect number =",
  sum(target_power_table$rejection_probability[(num_agent+num_category):(num_agent*num_category)]>0.8),
  " out of ", num_agent*num_category-num_agent-num_category+1
  )
```

### num_process = 50, num_simulation = 100 {.tabset}

#### beta hat

```{r,echo=FALSE,results = "asis"}
modelsummary::datasummary_skim(
  fmt = 3,
  beta_hat_table_num_process_50_num_agents_20_num_category_30[1:250]
  )
modelsummary::datasummary_skim(
  fmt = 3,
  beta_hat_table_num_process_50_num_agents_20_num_category_30[251:500]
  )
modelsummary::datasummary_skim(
  fmt = 3,
  beta_hat_table_num_process_50_num_agents_20_num_category_30[501:(num_agent*num_category)]
  )
```

#### Bias

```{r,echo=FALSE,results = "asis"}
modelsummary::datasummary_skim(
  fmt = 3,
  bias_table_num_process_50_num_agents_20_num_category_30[1:250]
  )
modelsummary::datasummary_skim(
  fmt = 3,
  bias_table_num_process_50_num_agents_20_num_category_30[251:500]
  )
modelsummary::datasummary_skim(
  fmt = 3,
  bias_table_num_process_50_num_agents_20_num_category_30[501:(num_agent*num_category)]
)
```

#### Power 

```{r,echo=FALSE,results = "asis"}
target_power_table <-
  cbind(
    colnames(t_stats_table_num_process_50_num_agents_20_num_category_30),
    colSums(t_stats_table_num_process_50_num_agents_20_num_category_30 > 1.96)/100
    ) %>% 
  tibble::as_tibble()
colnames(target_power_table) <-
  c(
    "coefficient",
    "rejection_probability"
    )
target_power_table %>% 
  kableExtra::kable() %>% 
  kableExtra::kable_styling()
cat(
  "Significant match effect number =",
  sum(target_power_table$rejection_probability[(num_agent+num_category):(num_agent*num_category)]>0.8),
  " out of ", num_agent*num_category-num_agent-num_category+1
  )
```

### num_process = 100, num_simulation = 100 {.tabset}

#### beta hat

```{r,echo=FALSE,results = "asis"}
modelsummary::datasummary_skim(
  fmt = 3,
  beta_hat_table_num_process_100_num_agents_20_num_category_30[1:250]
  )
modelsummary::datasummary_skim(
  fmt = 3,
  beta_hat_table_num_process_100_num_agents_20_num_category_30[251:500]
  )
modelsummary::datasummary_skim(
  fmt = 3,
  beta_hat_table_num_process_100_num_agents_20_num_category_30[501:(num_agent*num_category)]
  )
```

#### Bias

```{r,echo=FALSE,results = "asis"}
modelsummary::datasummary_skim(
  fmt = 3,
  bias_table_num_process_100_num_agents_20_num_category_30[1:250]
  )
modelsummary::datasummary_skim(
  fmt = 3,
  bias_table_num_process_100_num_agents_20_num_category_30[251:500]
  )
modelsummary::datasummary_skim(
  fmt = 3,
  bias_table_num_process_100_num_agents_20_num_category_30[501:(num_agent*num_category)]
  )
```

#### Power 

```{r,echo=FALSE,results = "asis"}
target_power_table <-
  cbind(
    colnames(t_stats_table_num_process_100_num_agents_20_num_category_30),
    colSums(t_stats_table_num_process_100_num_agents_20_num_category_30 > 1.96)/100
    ) %>% 
  tibble::as_tibble()
colnames(target_power_table) <-
  c(
    "coefficient",
    "rejection_probability"
    )
target_power_table %>% 
  kableExtra::kable() %>% 
  kableExtra::kable_styling()
cat(
  "Significant match effect number =",
  sum(target_power_table$rejection_probability[(num_agent+num_category):(num_agent*num_category)]>0.8),
  " out of ", num_agent*num_category-num_agent-num_category+1
  )
```