---
title: "02_estimate_tmss2007"
author: "Suguru Otani"
date: "2024-07-10"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# load {.tabset}

```{r, echo=FALSE,results = "asis"}
rm(list = ls())
library(magrittr)
library(ggplot2)
library(modelsummary) # for N in datasummary

result_benchmark_list <-
    readRDS(
      file = 
        here::here(
          paste(
            "output/",
            "result_benchmark_list",
            ".rds",
            sep = ""
          )
        )
    )
result_benchmark_n_teacher_1_list <-
    readRDS(
      file = 
        here::here(
          paste(
            "output/",
            "result_benchmark_n_teacher_1_list",
            ".rds",
            sep = ""
          )
        )
    )
result_benchmark_list_school_id_228 <-
    readRDS(
      file = 
        here::here(
          paste(
            "output/",
            "result_benchmark_list_school_id_228",
            ".rds",
            sep = ""
          )
        )
    )
result_school_id_228_constrained <-
    readRDS(
      file = 
        here::here(
          paste(
            "output/",
            "result_school_id_228_constrained",
            ".rds",
            sep = ""
          )
        )
    )

```

## whole sample 2007 {.tabset}

### result_benchmark_list (Without restriction)

```{r, echo=FALSE, results="asis"}
modelsummary::modelsummary(result_benchmark_list)
```

### result_constrained_model_list (With restriction)

```{r, echo=FALSE, results="asis"}

```

## whole sample n_teacher==1 2007 {.tabset}

### result_benchmark_list (Without restriction)

```{r, echo=FALSE, results="asis"}
modelsummary::modelsummary(result_benchmark_n_teacher_1_list)
```

### result_constrained_model_list (With restriction)

```{r, echo=FALSE, results="asis"}

```

## subsample 2007 (school_id_228) {.tabset}

### result_benchmark_list_school_id_228 (Without restriction)

```{r, echo=FALSE, results="asis"}
modelsummary::modelsummary(result_benchmark_list_school_id_228)
```

### result_constrained_model_list (With restriction)

```{r, echo=FALSE, results="asis"}
summary(result_school_id_228_constrained)

```